Project report

### 2018-02-18 ProjectReport/BigDataHomework.tex
update report
update readme

	\subsection{Trip Visualization (question C)}
	This trip visualization task is implemented in the function
  \texttt{visualize\_trips} and the created output is stored in the output
  folder in the \texttt{gmplot} directory. The trips list is shuffled in order
  to show random items, the first 5 of which are fetched for
  visualization. For each trip, we generate a tuple of longitudes and latitudes
  with the function \texttt{utils.idx\_to\_lonlat} which we pass on to the
  plotting function \texttt{utils.write\_group\_gml}. There, the longitude and
  latitude means are calculated as a visualization centroid for the produced map, and the gmplot
  library is used so as to visualize the respective point sequence. See the
  following figure for a visualization example.

@@

  To visualize the neighbours, the \texttt{visualize\_nns}
  function is used, where three lists are created:
  \begin{enumerate}
    \item a list with all the route points (longitudes and latitudes) of the
      test trip and its neighbours
    \item a list with the journey labels and the nn computation data
      \item a list with the colors with which to draw (all blue in this
        question).
      \end{enumerate}
      All this data is provided to the
      \texttt{utils.visualize\_point\_sequences} function. This function is
      supplied with point sequences with corresponding color sequences, and
      produces colored gml plot maps with the \texttt{write\_group\_gml}
      function. Each html output map is converted to a png image using a conversion tool in the \texttt{html\_to\_png} function, in
order to automate image creation from the generated maps (the tool is the
\texttt{rasterize.js} utility from the \texttt{phantomjs} module).
However we found the gml plot zoom difficult to automatically configure correctly so that
all points are visible, and thus the images in the report were fetched with a printscreen.
The converted images are used to create 6 subplots (1 test trip + k=5 nearest
neighbours). All plotting is done with the pylab package.

@@

 \begin{table}[H]
 	\centering
 	\begin{tabular}{|c|c|c|}
 		\hline
 		\textbf{Strategy}            & \textbf{Train Accuracy} & \textbf{Validation Accuracy} \\ \hline
 		\textbf{KNN}                 & 0.904                   & 0.861                        \\ \hline
 		\textbf{Logistic Regression} & 0.874                   & 0.831                        \\ \hline
 		\textbf{Random Forest}       & 0.995                   & 0.883                        \\ \hline
 	\end{tabular}
 \caption{Classification using KNN, logreg and random forest}
 \label{class}
 \end{table}

>>>>

	\subsection{Trip Visualization (question C)}
	This trip visualization task is implemented in the function
  \texttt{visualize\_trips} and the created output is stored in the output
  folder in the \texttt{gmplot} directory. The trips list is shuffled in order
  to show random items, the first 5 of which are fetched for
  visualization. For each trip, we generate a tuple of longitudes and latitudes
  with the function \texttt{utils.idx\_to\_lonlat} which we pass on to the
  plotting function \texttt{utils.write\_group\_gml}. There, the longitude and
  latitude means are calculated as a visualization centroid for the produced map, and the gmplot
  library is used so as to visualize the respective point sequence. Below, we present the resulting plots for the five selected trips.

@@

  To visualize the neighbours, the \texttt{visualize\_nns}
  function is used, where three lists are created:
  \begin{enumerate}
    \item a list with all the route points (longitudes and latitudes) of the
      test trip and its neighbours
    \item a list with the journey labels and the nn computation data
      \item a list with the colors with which to draw (all blue in this
        question)
      \end{enumerate}
      All this data is provided to the
      \texttt{utils.visualize\_point\_sequences} function. This function is
      supplied with point sequences with corresponding color sequences, and
      produces colored gml plot maps with the \texttt{write\_group\_gml}
      function. Each html output map is converted to a png image using a conversion tool in the \texttt{html\_to\_png} function, in
order to automate image creation from the generated maps (the tool is the
\texttt{rasterize.js} utility from the \texttt{phantomjs} module).
However we found the gml plot zoom difficult to automatically configure correctly so that all points are visible, and thus the images in the report were fetched with a printscreen. The converted images are used to create 6 subplots (1 test trip + k=5 nearest neighbours). All plotting is done with the pylab package.

In order to improve time performance, we have used a cache strategy exploiting the commutative property of the distance between two points. Therefore, we have used a dictionary storing a mapping of the point pair indices $(i,j)$ as well as $(j,i)$.

@@

 \begin{table}[H]
 	\centering
 	\begin{tabular}{|c|c|c|}
 		\hline
 		\textbf{Classifier}            & \textbf{Train Accuracy} & \textbf{Validation Accuracy} \\ \hline
 		\textbf{KNN}                 & 0.904                   & 0.861                        \\ \hline
 		\textbf{Logistic Regression} & 0.874                   & 0.831                        \\ \hline
 		\textbf{Random Forest}       & 0.995                   & 0.883                        \\ \hline
 	\end{tabular}
 \caption{Classification using KNN, logreg and random forest}
 \label{class}
 \end{table}
